---
title: "Restaurant analisyes"
output: html_document
---
#Discribtion

Historical data of a restaurant income.

```{r}
#package required
library(tidyverse)
library(dplyr)
library(ggplot2)
library(viridis)
library(RColorBrewer)

#data
food <- read.csv("Food_demand.csv")

```

```{r}

#get to know your data
summary(food)
glimpse(food)
```

#How much is the restaurant income ?

```{r}
income <- sum(food$checkout_price)
```

#What is minimum and maximum check out price Weakly?
```{r}
 weeks<- food %>% 
          group_by(week) %>% 
          summarise( weeklyCheckout = sum(checkout_price))

max(weeks$weeklyCheckout)
min(weeks$weeklyCheckout)
```
 Overall income of 145 centers is 654277.89 and the weekly income variance between 7613 and 1403 .
 
#Which dish gives the most income?
```{r}

mealID <- food %>% 
         group_by(meal_id) %>% 
         summarise(checkoutPrice = sum(checkout_price))

ggplot(mealID, aes(meal_id, checkoutPrice ))+
  geom_jitter(shape = 16,width = 0.6, alpha = 0.5,
              size = 2, color = plasma(51) ) +
  labs(title = "Sum of Checkout Price",
       x ="Meak ID",
       y = "Checkout Price")+
  theme_bw() +
  theme(legend.position = "none",
        strip.background = element_blank()) 

range(mealID$checkoutPrice)

```
There are 51 types of dishes and their income to the company range between 3193.7 and 31373 .
#How stable is the weekly chick out price ?
```{r}

weeklyChekout <- food %>% 
                 group_by(week) %>% 
                 summarise(checkoutPrice = sum(checkout_price))

ggplot(weeklyChekout, aes(x= checkoutPrice))+
  geom_histogram(fill = "#7570B3") +
  labs(title = "Weely Check out price",
       x ="Week",
       y = "Check out") +
  theme_test() +
  theme(rect = element_blank())

#mean
checkoutMean <- mean(weeklyChekout$checkoutPrice)

#sd
checkoutSd <- sd(weeklyChekout$checkoutPrice)

# SEM 
SEM <- checkoutSd/sqrt(length(weeklyChekout))

# 95% CI
CI_lower <- checkoutMean - (1.96 * SEM)
CI_upper <- checkoutMean + (1.96 * SEM)


```

#Which restaurant center is more popular by the number of orders?

```{r}

centerID <- food %>% 
            group_by(center_id) %>%
            filter(num_orders <5000) %>% 
            summarise(numOrders = sum(num_orders))
length(food$center_id)
 
ggplot(centerID, aes(center_id, numOrders))+
  geom_jitter(shape = 16,width = 0.6, alpha = 0.5,
              size = 2, color = plasma(77) ) +
  labs(title = "Sum of Number of Oreders",
       x ="Center ID",
       y = "Number of orders")+
  theme_bw() +
  theme(legend.position = "none",
        strip.background = element_blank()) 


max(centerID$numOrders)

min(centerID$numOrders)


```
There is high difference between the number of orders between the centers.

#How does the centerID influence the number of orders ?
```{r}

lm_food <- lm(checkout_price ~ center_id, data = food)
summary(lm_food)
coef(lm_food)
anova(lm_food)
```

#How is the weekly orders of one center ?
```{r}

centerIncome10 <- food %>% 
  group_by(week) %>% 
  filter(center_id == 10) %>% 
  summarise(num_orders)  

ggplot(centerIncome10, aes(week, num_orders))+
  geom_point(color = plasma(30)) +
  geom_smooth(method = "lm", se =FALSE, color = 'black') + 
  labs(title = "Number of Oreders of One Center",
       x ="Week",
       y = "Number of orders")+
  theme_minimal() +
  theme(legend.position = "non")


mean(centerIncome10$num_orders)

#Variance
sd(centerIncome10$num_orders)
```
In this center the liner is going up by variation of 599.

#another center
```{r}

centerIncome23 <- food %>% 
  group_by(week) %>% 
  filter(center_id == 23) %>% 
  summarise(num_orders)

ggplot(centerIncome23, aes(week, num_orders))+
  geom_point(color = plasma(31)) +
  geom_smooth(method = "lm", se =FALSE, color = 'black') + 
  labs(title = "Number of Oreders of One Center",
       x ="Week",
       y = "Number of orders")+
  theme_minimal() +
  theme(legend.position = "non")

mean(centerIncome23$num_orders)

#Variance
sd(centerIncome23$num_orders)

```

#all centers
```{r}

centerIncomeAll <- food %>% 
  group_by(week) %>%
  filter(num_orders < 1000) %>% 
  summarise(allOrders = sum(num_orders))

ggplot(centerIncomeAll, aes(week, allOrders))+
  geom_point(color = plasma(145)) +
  geom_smooth(method = "lm", se =FALSE, color = 'black') + 
  labs(title = "Number of Oreders of All Center",
       x ="Week",
       y = "Number of orders")+
  theme_minimal() +
  theme(legend.position = "non")
  
mean(centerIncomeAll$num_orders)

#Variance 

sd(centerIncomeAll$allOrders)
```
We noticed that the orders are going slightly up in general through the time with variation of 1010.7 


