---
title: "Food demands"
output: html_document
---

#About the data

Given the following information, the task is to predict the number of orders for the next 10 weeks for the meal combinations, which are:

Historical data of demand for a product-center combination (Weeks: 1 to 145)
Product(Meal) features such as category, sub-category, current price and discount
Information for fulfillment centers like center area, city information, etc.The dataset, “Food Demand Forecasting” was released by an American professional services firm, Genpact for a Machine Learning Hackthon.

Source:
https://github.com/SaiPrasath-S/DemandPrediction

#Questions need to be answered:
1-What are the main controlling reasons determine the number of orders
2-What are the predicted numbers and type of dishes each day (use the mean).
#Data and libraries

```{r}
#package required
library(rsample)
library(tidyverse)
library(stats)
library(dplyr)
library(caret)

#data
food <- read.csv("Food_demand.csv")
# initial dimension
dim(food)

# response variable
head(food$num_orders)

```
##Data splitting and distribution.

```{r}
            
set.seed(123) # for reproducibility
split <- initial_split(food, strata = "num_orders", prop = 0.7)
food_train <- training(split)
food_test  <- testing(split)

#Model with lm()

lm_food <- lm(num_orders ~ checkout_price, data = food_train)
summary(lm_food)

lm_food2 <- lm(num_orders ~ checkout_price + base_price, data = food_train)
summary(lm_food2)

lm_food3 <- lm(num_orders ~ ., data = food_train)
summary(lm_food3)

coef(lm_food) 
coef(lm_food2) 

```
#knn
```{r}
# Specify resampling strategy
cv <- trainControl(
  method = "repeatedcv", 
  number = 10, 
  repeats = 5
)

# Create grid of hyperparameter values
hyper_grid <- expand.grid(k = seq(2, 25, by = 1))

# Tune a knn model using grid search
knn_fit <- train(
  num_orders ~ checkout_price, 
  data = food_train, 
  method = "knn", 
  trControl = cv, 
  tuneGrid = hyper_grid,
  metric = "RMSE"
)

# 6. evaluate results
# print model results
knn_fit

# plot cross validation results
ggplot(knn_fit$results, aes(k, RMSE)) + 
  geom_line() +
  geom_point() +
  scale_y_continuous(labels = scales::dollar)
```
#Plot of the top 10 most influential features.

```{r prereqs-data}
# we use model.matrix(...)[, -1] to discard the intercept
X <- model.matrix(num_orders ~ ., food_train)[, -1]

# transform y with log transformation
Y <- log(food_train$num_orders)

# perform resampling
set.seed(123)
cv_glmnet <- train(
  x = X,
  y = Y,
  method = "glmnet",
  preProc = c("zv", "center", "scale"),
  trControl = trainControl(method = "cv", number = 10),
  tuneLength = 10
)

vip(cv_glmnet, num_features = 20, geom = "point")

```


# Feature effects
```{r}
set.seed(123)
cv_model2 <- train(
  num_orders ~ checkout_price, 
  data = food_train, 
  method = "lm",
  trControl = cv
  )

# linear regression model

p1 <- pdp::partial(cv_model2, pred.var = "checkout_price", grid.resolution = 10) %>% 
  ggplot(aes(checkout_price, yhat)) +
  geom_line()
p1

set.seed(123)
cv_model3 <- train(
  num_orders ~ homepage_featured, 
  data = food_train, 
  method = "lm",
  trControl = cv
  )

p2 <- pdp::partial(cv_model3, pred.var = "base_price", grid.resolution = 10) %>% 
  ggplot(aes(base_price, yhat)) +
  geom_line()
p2


#Assess the interaction of the top 2 predictors:
pdp::partial(
  cv_model2,
  pred.var = c("checkout_price", "base_price"),
  grid.resolution = 10
  ) %>% 
  pdp::plotPartial(
    levelplot = FALSE,
    zlab = "number of orders", 
    drape = TRUE, 
    colorkey = TRUE, 
    screen = list(z = -20, x = -60)
    )
```
# Tuning parameters
```{r}
# perform resampling
# tuning grid
hyper_grid <- expand.grid(
  nprune = seq(2, 50, length.out = 10) %>% floor(),
  degree = 1:3
)

set.seed(123)
cv_mars <- train(
  num_orders ~ ., 
  data = food_train, 
  trControl = trainControl(method = "cv", number = 10),
  method = "earth",
  tuneGrid = hyper_grid,
  metric = "RMSE"
  )

# best model
cv_mars$results %>%
  filter(
    nprune == cv_mars$bestTune$nprune,
    degree == cv_mars$bestTune$degree
    )

# plot results
plot(cv_mars)
```


#Model concerns
```{r}
#Linear relationship
ggplot(food_train, aes(checkout_price, base_price)) + 
  geom_point(size = 1, alpha = .4) + 
  geom_smooth(method = "lm", se = FALSE) +
  scale_y_log10("Number of orders", labels = scales::dollar) +
  xlab("price") +
  ggtitle(paste("near-linear relationship."))

```




